Pillar 2 - Topic Modeling

### 2019-01-10 Pillar 2 - Topic Modeling.Rmd
Function to visualize LDA

>>>>

```{r function visualize_LDA, eval = F}
visualize_LDA <- function(results, id_plot = "test", facet = F, topic_names = NULL){

  # Setup
  topic_letter <- tibble(topic_number = 1:26,
                         topic_letter = c(topic_names,
                                          paste("Topic", LETTERS[(length(topic_names)+1) : 26])))

  # Beta Distribution: term-topic
  term_topic <- tidy(results, matrix = "beta") %>%
    left_join(topic_letter, by = c("topic" = "topic_number")) %>%
    mutate(topic = topic_letter) %>%
    select(-topic_letter)

  term_topic %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup %>%
    ggplot(aes(x = reorder_within(term, by = beta, within = topic), y = beta, fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, scales = "free") +
    scale_x_reordered() +
    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
    coord_flip() +
    theme_light() +
    theme(plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "beta.jpeg"),
         width = 15, height = 10, path = "Plots")

  # Gamma Distribution: document-topic
  doc_topic <- tidy(results, matrix = "gamma") %>%
    left_join(topic_letter, by = c("topic" = "topic_number")) %>%
    mutate(topic = topic_letter,
           facet = document) %>%
    select(-c(topic_letter, document))

  if(facet) doc_topic <- separate(doc_topic, facet, c("document", "facet"), sep = "_") %>%
    add_count(facet) %>%
    group_by(facet, topic) %>%
    summarise(gamma = sum(gamma)) %>%
    ungroup

  # Plot 1
  doc_topic %>%
    filter(gamma > 0.05) %>%
    ggplot(aes(reorder_within(facet, by = gamma, within = topic), y = gamma, fill = facet)) +
    geom_col(show.legend = F) +
    facet_rep_wrap(~ topic, scales = "free",
                   repeat.tick.labels = "bottom") +
    scale_x_reordered() +
    coord_flip() +
    labs(x = "(Group of) Courses", y = "Gamma", title = "Main Courses/Clusters of each Topic") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "gamma1.jpeg"),
         width = 15, height = 10, path = "Plots")

  # Plot 2
  doc_topic %>%
    filter(gamma > 0.05) %>%
    ggplot(aes(reorder_within(topic, by = gamma, within = facet), y = gamma, fill = topic)) +
    geom_col(show.legend = F) +
    facet_rep_wrap(~ facet, scales = "free",
                   repeat.tick.labels = "bottom") +
    scale_x_reordered() +
    coord_flip() +
    labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "gamma2.jpeg"),
         width = 15, height = 10, path = "Plots")

}
```
